Experiment 2 of 4

### 2016-09-26 experiments/e2/writeup/e2.Rmd
finished updated stats for e2

```{r rtplot, fig.width=5, fig.height=3}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=3, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number) 
rtplot
```

```{r blplot, fig.width=5, fig.height=2.5}
bldata$Condition <- as.factor(paste(sep=':', bldata$Vagueness, bldata$Number))
bldata$response_category <- relevel(bldata$response_category, ref = 'expected')
blplot=ggplot(bldata) + 
  geom_bar(aes(Vagueness, fill=response_category), position = 'dodge') +
  #geom_errorbar() +
  facet_wrap(nrow=1,~Number) +
  scale_fill_grey(name="Response Type") +
  xlab(" ") +
  ggtitle("Response Type") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'))
blplot
```

<!-- ```{r} -->
<!-- dd$response_category <- relevel(dd$response_category, ref = 'expected') -->
<!-- barplot(table(dd$Vagueness,dd$response_category), beside=TRUE, legend=TRUE, space=c(0,.5)) -->
<!-- ``` -->

<!-- , ymin=isBorderlineNormed-ci, ymax=isBorderlineNormed+ci,  group=Condition, fill=Condition)) + -->

>>>>

```{r rtplot, fig.width=5, fig.height=3, echo=F}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=3, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number) 
rtplot
```

```{r blplot, fig.width=5, fig.height=2.5, echo=F}
bldata$Condition <- as.factor(paste(sep=':', bldata$Vagueness, bldata$Number))
bldata$response_category <- relevel(bldata$response_category, ref = 'expected')
blplot=ggplot(bldata) + 
  geom_bar(aes(Vagueness, fill=response_category), position = 'dodge') +
  #geom_errorbar() +
  facet_wrap(nrow=1,~Number) +
  scale_fill_grey(name="Response Type") +
  xlab(" ") +
  ggtitle("Response Type") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'))
blplot
```

```{r rtlmer, cache=TRUE}
rtlmer = lmerTest::lmer(data=rtdata,
                        RT_log ~ c_Vag * c_Num + c_Itm +
                          (1 + c_Vag * c_Num + c_Itm | Subject))
```

```{r rtlmersummaryxtable, results='asis', cache=TRUE}
print(xtable(summary(rtlmer)$coef, digits=c(0,2,2,1,1,4)),type='html')
```

```{r seplmersfornum, results='asis', cache=TRUE}
s1 <- subset(rtdata, subset=Number=='Numeric')
s1lm <- lmerTest::lmer(data=s1, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s1lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r seplmersforvag, results='asis', cache=TRUE}
s2 <- subset(rtdata, subset=Number=='Verbal')
s2lm <- lmerTest::lmer(data=s2, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s2lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r bllmer, cache=TRUE}
bllmer = lme4::glmer(data=bldata,
                        isBorderline ~ c_Vag * c_Num + c_Itm +
                          (1 + c_Vag * c_Num + c_Itm | Subject),
                        family="binomial", control = glmerControl(optimizer = "bobyqa"))
```

```{r bllmersummaryxtable, results='asis', cache=TRUE}
print(xtable(summary(bllmer)$coef, digits=c(0,2,2,1,4)),type='html')
```
